---
title: "hw4_bm_wq2160"
author: "Wenshan Qu (wq2160)"
date: "11/11/2021"
output: html_document
---

```{r include = FALSE}
library(tidyverse)
```

## Problem 1

We want to prove $\sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}} (y_{ij} - \bar{\bar{y}})^2  = \sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}} (y_{ij} - \bar{y_{l}})^2 + \sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}} (\bar{y_{l}} - \bar{\bar{y}})^2$

Which could also be seen as $TotalSS = WithinSS + BetweenSS$

Note that:

$k$: number of groups;

$n_{i}$: number of observations in the $i^{th}$ group;

$y_{ij}$: denotes the observation of the $j^{th}$ subject from the $i^{th}$ group;

$\bar{\bar{y}}$: grand mean;

$\bar{y_{l}}$: mean from the $i^{th}$ group.


Proof:

$TotalSS = \sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}} (y_{ij} - \bar{\bar{y}})^2 = \sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}}(y_{ij} - \bar{y_{l}} + \bar{y_{l}} - \bar{\bar{y}})^2$

$= \sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}}[(y_{ij} - \bar{y_{l}}) + (\bar{y_{l}} - \bar{\bar{y}})]^2$

$= \sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}}[(y_{ij} - \bar{y_{l}})^2 + (\bar{y_{l}} - \bar{\bar{y}})^2 + 2(\bar{y_{l}} - \bar{\bar{y}})(y_{ij} - \bar{y_{l}})]$

$= \sum_{i = 1}^{k} [\sum_{j = 1}^{n_{i}}(y_{ij} - \bar{y_{l}})^2 + \sum_{j = 1}^{n_{i}}(\bar{y_{l}} - \bar{\bar{y}})^2 + 2(\bar{y_{l}} - \bar{\bar{y}})\sum_{j = 1}^{n_{i}}(y_{ij} - \bar{y_{l}})]$

(Becasue $\bar{y_{l}} = \frac{\sum_{j = 1}^{n_{i}}y_{ij}}{n_{i}}$, then $\sum_{j = 1}^{n_{i}}(y_{ij} - \bar{y_{l}}) = \sum_{j = 1}^{n_{i}}y_{ij} - n_{i}\bar{y_{l}} = 0$,)

$= \sum_{i = 1}^{k} [\sum_{j = 1}^{n_{i}}(y_{ij} - \bar{y_{l}})^2 + \sum_{j = 1}^{n_{i}}(\bar{y_{l}} - \bar{\bar{y}})^2]$

$= \sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}} (y_{ij} - \bar{y_{l}})^2 + \sum_{i = 1}^{k} \sum_{j = 1}^{n_{i}} (\bar{y_{l}} - \bar{\bar{y}})^2$

$= WithinSS + BetweenSS$

## Problem 2

```{r}

```

